Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-06-08 SupportingInformation.Rmd
adding loecke_data description

Carbon and nitrogen in soil at many locations across CONUS (Terry to augment this description). The raw data are shown in Figure \ref{fig_raw_cop_soilCN}(A). The copula is shown in Figure \ref{fig_raw_cop_soilCN}(B).

@@

## Methane-flux data  \label{Methane_data}
   * Methane-flux at many locations (Prof. Terry to augment this description).
   * We threw out all locations that had fewer than 50 dates data.

>>>>

To explore the correlation of soil organic C and total soil N across a wide geographic range (conterminous
US), ecosystem type, and traceable methodology we used the RaCA (Rapid Carbon Assessment)
database [@Wills2014, **or Wills and Loecke pending???**]. Specifically, the soil organic C and total soil N
stocks (Mg C or N m$^{-2}$ ) to 1m of soil depth from the central pedon of the **6???** sites were included in this
study.

The raw data are shown in Figure \ref{fig_raw_cop_soilCN}(A). The copula is shown in Figure \ref{fig_raw_cop_soilCN}(B).

@@

## Methane-flux data  \label{Methane_data}

Methane ($CH_{4}$) fluxes between the soil or water surface and the troposphere were measured at the
Great Miami Wetland Mitigation Bank ($36^{\circ}46^{'}51^{''}$ N, $84^{\circ}20^{'}26^{''}$ W) in Trotwood, Montgomery County, Ohio. Additional information on the history of the site and soil types is detailed in @Jarecke2016. Briefly, the closed static flux chamber method was used [@Holland1999] to measure $CH_{4}$ fluxes at **???(check after filtering to 50 fluxes)** locations across a hydrologic gradient (upland to seasonal wetland) at
daily to weekly interval from September 2015 to September 2016. **See and Smyth et al, pending for
additional details???** on greenhouse gas flux methods for this site.

* We threw out all locations that had fewer than 50 dates data.
